The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
todo update dates in manuscript

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception). Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier et al. 2019) and spatial (Webber et al. unpublished data) variation in social networks. In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free. Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al. 2009). The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou. We therefore partitioned data into two discrete seasons: summer (3 August - 17 October) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al. 2019).

@@

### Landscape ecology

>>>>

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception). Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier et al. 2019) and spatial (Webber et al. unpublished data) variation in social networks. In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free. Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al. 2009). The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou. We therefore partitioned data into two discrete seasons: <!-- TODO update these --> *summer (3 August - 17 October) and winter (1 January – 16 March)* based on caribou socioecology (Peignier et al. 2019).

@@

### Habitat selection and space use

Mayor et al. 2009 paper

MRSF Laforge paper

van Beest et al. 2014 scale paper

1st/2nd/3rd order selection blah blah

Paper: Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
